Left-linear rules in adhesive categories

### 2024-02-12 icalp/fusione.tex
examples

\begin{example}
  Consider the rewriting system used as running example (rules in
  Fig.~\ref{fi:rules}. Assume to add a fourth rule $\rho_4$ as in
  Fig.~\ref{fi:rule-cas} and consider the derivation.
\end{example}

>>>>

\begin{example}
  Consider the rewriting system used as running example (rules in
  Fig.~\ref{fi:rules}. Assume to add rules $\rho_3$ and $\rho_4$ as
  depicted in Fig.~\ref{fi:rules-cas}. Consider the derivation
  $\der{F}$ in Fig.~\ref{fi:derF}. Observe that rule $\rho_4$ to be
  applied needs a self loop on node $12$. This can be generated either
  by $\rho_3$ or $\rho_1$ merging nodes $1$ and $2$, hence at least
  one of them must precede the application of $\rho_4$. Indeed, in $\der{E}$ it can be easily seen that the second and third step applying $\rho_1$ and $\rho_3$ are independent. However, we could switch twice the application of $\rho_3$, bringing it in the last position, obtaining a derivation $\der{F}'$ (see {\color{red} DA FINIRE, se ci sta}), where the applications of  $\rho_1$ and $\rho_3$ are no longer independent.

  \begin{figure}
    \input{Figure/rules-cas.tex}    
    \caption{Additional rules.}
    \label{fi:rules-cas}
  \end{figure}

  \begin{figure}
    \input{Figure/derF.tex}    
    \caption{A derivation $\der{F}$.} 
    \label{fi:derF}
  \end{figure}
\end{example}
